---
title: "rfinal"
output: pdf_document
---

```{r, message = FALSE}
library(tidyverse)
library(dplyr)
library(boot)
library(aod)
library(ggplot2)
#card <- read.csv("/Users/srinivasansathiamurthy/Desktop/carbontax.csv")
carbind <- read.csv("/Users/srinivasansathiamurthy/Desktop/carbonprice.csv")
climate <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_19_DS2_en_csv_v2_3159902.csv")
econgrowth <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_3_DS2_en_csv_v2_3163364.csv")
energy <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_5_DS2_en_csv_v2_3161037.csv")
externdebt <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_20_DS2_en_csv_v2_3163387.csv")
govtdebt <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_13_DS2_en_csv_v2_3163417.csv")
urban <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_16_DS2_en_csv_v2_3161141.csv")
techrnd <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_14_DS2_en_csv_v2_3163423.csv")
poverty <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_11_DS2_en_csv_v2_3159271.csv")
trade <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_21_DS2_en_csv_v2_3163432.csv")
labor <- read.csv("/Users/srinivasansathiamurthy/Desktop/API_10_DS2_en_csv_v2_3163427.csv")
```

## R Markdown

control for country dummies
- we have time varied 
we can include country specific variables (whether or not it is that country or not)
so in each data point "is this iran or not, is this afghanistan or not"
use the plm package for that
main_slides_rs05_practice
daily_notes_rs14_nov22

just pick the variables you really care about
think about your punch line
- figure out which variables matter and which don't (use t-statistic on multilinear regression)

meet again on wednesday with prof kang

logistic model no neural network (not enough data)

```{r}
##########################################################################only use data from 2010 to 2017
climate_C02kt<- climate[climate$Indicator.Name=="CO2 emissions (kt)",]
climate_renewpercent<- climate[climate$Indicator.Name=="Renewable energy consumption (% of total final energy consumption)",]
econind_gdpcap <- econgrowth[econgrowth$Indicator.Name=="GDP per capita (current US$)",]
urban_airpolpop <- urban[urban$Indicator.Name=="PM2.5 air pollution, population exposed to levels exceeding WHO guideline value (% of total)",]
urban_pop<- urban[urban$Indicator.Name=="Urban population (% of total population)",]
trade_fuelimport <- trade[trade$Indicator.Name=="Fuel imports (% of merchandise imports)",]
trade_fuelexport <- trade[trade$Indicator.Name=="Fuel exports (% of merchandise exports)",]
labor_emp <- labor[labor$Indicator.Name=="Unemployment, total (% of total labor force) (modeled ILO estimate)",]

#maybe do some underlying testing on these countries to see biases and stuff?
nacountryvec = unique(c(econind_gdpcap$Country.Name[is.na(econind_gdpcap$X2018)], urban_airpolpop$Country.Name[is.na(urban_airpolpop$X2010)], urban_pop$Country.Name[is.na(urban_pop$X2014)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2017)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2012)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2015)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2013)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2011)], trade_fuelimport$Country.Name[is.na(trade_fuelimport$X2010)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2017)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2012)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2015)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2013)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2011)], trade_fuelexport$Country.Name[is.na(trade_fuelexport$X2010)], labor_emp$Country.Name[is.na(labor_emp$X2010)], labor_emp$Country.Name[is.na(labor_emp$X2017)]))
carbind2 <- carbind[ ! carbind$Country.Name %in% nacountryvec, ]
carbind2 <- subset(carbind2, select = -c(X, X1990, X1991, X1992, X1993, X1994, X1995, X1996, X1997, X1998, X1999, X2000, X2001, X2002, X2003, X2004, X2005, X2006, X2007, X2008, X2009, X2018, X2019, X2020, X2021))
carbind2 <- carbind2[!(carbind2$Country.Name=="Bahamas"| carbind2$Country.Name=="Gambia" | carbind2$Country.Name=="Hong Kong"),] 

ind <- vector()
C02ktvec <- vector()
renewpercentvec <- vector()
gdpcap <- vector()
airpolpop <- vector()
pop <- vector()
fuelimport <- vector()
fuelexport <- vector()
emp <- vector()
name <- vector()

for(j in 1:129){
  for(i in 55:62){  
    ind <- c(ind, carbind2[j, i-52])
    C02ktvec <- c(C02ktvec, log(climate_C02kt[climate_C02kt$Country.Name== carbind2[j, 1], i]))
    renewpercentvec<- c(renewpercentvec, climate_renewpercent[climate_renewpercent$Country.Name== carbind2[j, 1], i])
    gdpcap <- c(gdpcap, log(econind_gdpcap[econind_gdpcap$Country.Name== carbind2[j, 1], i]))
    airpolpop <-c(airpolpop, urban_airpolpop[urban_airpolpop$Country.Name== carbind2[j, 1], i])
    pop <- c(pop, log(urban_pop[urban_pop$Country.Name== carbind2[j, 1], i]))
    fuelimport <-c(fuelimport, trade_fuelimport[trade_fuelimport$Country.Name== carbind2[j, 1], i])
    fuelexport <- c(fuelexport, trade_fuelexport[trade_fuelexport$Country.Name== carbind2[j, 1], i])
    emp<- c(emp, labor_emp[labor_emp$Country.Name== carbind2[j, 1], i])
  }
}

logitdata<- data.frame(ind, C02ktvec, renewpercentvec, gdpcap, airpolpop,pop,  fuelimport, fuelexport, emp)
logitdata

wt<- vector()
for(i in 1:1032){
  wt<- append(wt, 6.478*(1-logitdata$ind[i])+1)
}
logitdata$wt = wt
##emp, fuelimport, renewpercentvec coefficients ended up not being statistically significant and are pretty much irrelevant magnitude wise as well
mylogit <- glm(ind ~ C02ktvec + gdpcap+airpolpop+fuelexport, weights=wt, data = logitdata, family = binomial)
summary(mylogit)
exp(coef(mylogit))

mylogit2 <- glm(ind ~ C02ktvec + gdpcap+airpolpop+fuelexport+emp+fuelimport+renewpercentvec, weights=wt, data = logitdata, family = binomial)
summary(mylogit2)
exp(coef(mylogit2))

```

dealing with reverse causality:
thinking energy usage is affecting carbon tax or vice versa
lag value: carbon tax policy this year is affected by predictors of last year (how to do this?)
- create a vector: 
given country sort it chronologically

(done)
don't need to worry too much about including variables that are statistically significant
not that concerned about fitting
we want to include more variables in the regression to take care of counfounding vector!! (put everything in)

(need to do)
potential different specifications:
- linear regression also good
- show linear too! (same specifications) [include fixed effects]
  - **country dummy variables and year dummy variables**
  
  year as x axis and carbon tax as y axis
